### 2015-05-26 writing/SNLI paper/entailment_eval.tex
Update the baselines section

\subsection{Standard entailment models}
We evaluate a number of strong baselines on the SNLI corpus.
The first class of baselines use models from the Excitement Open
  Platform (EOP,
  \citealt{pado2014design,magnini2014excitement})
  -- an open source platform for RTE research which
  is distributed alongside a number of RTE pipelines.
We additionally evaluate against a both an unlexicalized and lexicalized
  classifier with straightforward feature sets.
\todo{some meaningful insight from \#s}

@@

% methodology
We convert the 3-way classification task in SNLI into the RTE setting
  by labeling both the \unknown\ and \contradiction\
  labels as negative entailment, and treating the \entailment\ label as
  the positive entailment.
This creates a biased dataset of 66\% negative examples.
% we report the best results from each class
We run each of the 9 algorithms distributed with EOP on the 2-class
  SNLI dataset, and report results for the best edit distance 
  configuration and the best classifier based configuration, as
  determined by performance on the development set.
\todo{we may not have CPU time for this}.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{SNLI}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{68.0} & \t{38.7} & \t{49.3} & \t{73.5} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
For comparision, results are also reported on the RTE-3 dataset.
\todo{numbers are still dev.}
}
\end{table}
%
% END EOP RESULTS TABLE
%

% the best systems
We report results in \reftab{eopresults}.
The best edit distance algorithm tunes the the weight of the three 
  case-insensitive edit distance operations on the training set, 
  after removing stop words.
The best classifier-based system \todo{does something}.
\todo{some insight from results}.

%
% Lexicalized Classifier
%
\paragraph{Lexicalized Classifier}
Unlike the RTE datasets, SNLI's size allows approaches which make use of
  rich lexicalized features.
We implmement a lexicalized classifier to provide a strong baseline for future work
  on the dataset.
Our classifier implements 6 features:
\begin{enumerate}  % TODO(gabor) This takes up way too much space
\setlength\itemsep{0em}
  \item the BLEU score of the \hypothesis\ with respect
  to the \premise, using an n-gram length between 1 and 4.

@@

  \item The overlap between words in the \premise\ and \hypothesis. This is counted
  both as an absolute count and a percentage of possible overlap, and is computed
  both over all words and over just nouns, verbs, adjectives, and adverbs.

  \item For every pair of words across the \premise\ and \hypothesis\ which share a 
  POS tag, an indicator feature over the two words.

  \item For every pair of bigrams across the \premise\ and \hypothesis\ which share a 
  POS tag, an indicator feature over the two bigrams.

  \item An indicator for every unigram and bigram in the \hypothesis.
\end{enumerate}

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceM}c}
\hline
\textbf{System} & \b{Dev} & \multicolumn{4}{c}{\b{Test}} \\
 & \t{Acc.} & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Lexicalized}            & \t{??.?} & \t{79.4} & \t{82.3} & \t{80.9} & \t{78.2} \\
\t{Unigrams Only}          & \t{??.?} & \t{71.1} & \t{77.7} & \t{74.3} & \t{71.6} \\
\t{Unlexicalized}          & \t{??.?} & \t{56.0} & \t{64.4} & \t{59.9} & \t{50.39} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
Accuracy on the 2-class and 3-class SNLI dataset, as well as precision/recall
  on the 2-class task to allow for comparision with the RTE systems.
Ablation results are reported for models lacking bigram features and lacking all lexical
  features.
\todo{fill in dev numbers}
}
\end{table}
%
% END BOW RESULTS TABLE
%

% Commenting out until PDF available. -S
% Running 'make' should generate PDF from gnuplot
\Fig{learning_curves_bow.pdf}{0.6}{bowlearncurve}{
A learning curve for the lexicalized and unlexicalized baseline classifiers,
plotted on a log scale.
Note the y axis starting at a random-chance accuracy of 33\%.
\todo{numbers are approx.}
}

@@

>>>>

\subsection{Standard entailment models}
We evaluate a number of strong baselines on the SNLI corpus.
The first class of baselines use models from the Excitement Open
  Platform (EOP,
  \citealt{pado2014design,magnini2014excitement})
  -- an open source platform for RTE research.
%  which
%  is distributed alongside a number of RTE pipelines.
We additionally evaluate against a strong classifier-based baseline based on
  both  unlexicalized and lexicalized features.

@@

%% methodology
%We convert the 3-way classification task in SNLI into the RTE setting
%  by labeling both the \unknown\ and \contradiction\
%  labels as negative entailment, and treating the \entailment\ label as
%  the positive entailment.
%This creates a biased dataset of 66\% negative examples.
% we report the best results from each class
We run the top performing edit-distance based algorithm and the top
  performing classifier-based algorithm on the SNLI test set, as
  determined by performance on the development set.
Note that these models were run using the default configuration
  with minimal tuning.
The results should therefore be taken as a strong baseline for
  RTE-style approaches to the problem, rather than necessarily
  representing the state-of-the-art system's performance on the
  task.
%We run each of the 9 algorithms distributed with EOP on the 2-class
%  SNLI dataset, and report results for the best edit distance 
%  configuration and the best classifier based configuration, as
%  determined by performance on the development set.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{SNLI}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{67.9} & \t{38.7} & \t{49.3} & \t{7X.X} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
3-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
In order to calibrate the difficulty of the dataset against the 
  classical RTE problems, results are also reported on the (2-class) 
  RTE-3 dataset.
\todo{numbers are still dev.}
}
\end{table}
%
% END EOP RESULTS TABLE
%

% the best systems
We report results in \reftab{eopresults}.
The best edit distance algorithm tunes the the weight of the three 
  case-insensitive edit distance operations on the training set, 
  after removing stop words.
The best classifier-based system makes use of information from
  WordNet \cite{miller1995wordnet} and VerbOcean
  \cite{chklovski2004verbocean}, and makes use of features
  based on tree patterns and dependency tree skeletons
  \cite{wang2007recognizing}.
Unsurprisingly, the classification-based approach outperforms simple
  edit distance metrics, and performs quite well despite relatively
  little lexicalization.

% TODO(Sam): Can you add these to the Bibtex?
%
%@article{miller1995wordnet,
%  title={{W}ord{N}et: a lexical database for English},
%  author={Miller, George A},
%  journal={Communications of the ACM},
%  volume={38},
%  number={11},
%  pages={39--41},
%  year={1995},
%  publisher={ACM}
%}
%
%@inproceedings{chklovski2004verbocean,
%  title={VerbOcean: Mining the Web for Fine-Grained Semantic Verb Relations.},
%  author={Chklovski, Timothy and Pantel, Patrick},
%  booktitle={EMNLP},
%  year={2004}
%}
%
%@inproceedings{wang2007recognizing,
%  title={Recognizing textual entailment using sentence similarity based on dependency tree skeletons},
%  author={Wang, Rui and Neumann, G{\"u}nter},
%  booktitle={ACL-PASCAL Workshop on Textual Entailment and Paraphrasing},
%  year={2007},
%}

%
% Lexicalized Classifier
%
\paragraph{Lexicalized Classifier}
Unlike the RTE datasets, SNLI's size allows approaches which make use of
  rich lexicalized features.
We implmement such a lexicalized classifier as a strong baseline 
  for the task.
Our classifier implements 6 features:
\begin{enumerate}
\setlength\itemsep{-0.25em}
  \item the BLEU score of the \hypothesis\ with respect
  to the \premise, using an n-gram length between 1 and 4.

@@

  \item The overlap between words in the \premise\ and \hypothesis. We include
  both as an absolute count and a percentage of possible overlap, and compute
  the count both over all words and over just nouns, verbs, adjectives, 
  and adverbs.

  \item\label{lst:ngram} An indicator for every unigram and bigram in the \hypothesis.

  \item\label{lst:unigram} Cross-unigrams: for every pair of words across the \premise\ and \hypothesis\ which share a 
  POS tag, an indicator feature over the two words.

  \item\label{lst:bigram} Cross-bigrams: for every pair of bigrams across the \premise\ and \hypothesis\ which share a 
  POS tag, an indicator feature over the two bigrams.
\end{enumerate}

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceM}c}
\hline
\textbf{System} & \b{Dev} & \multicolumn{4}{c}{\b{Test}} \\
 & \t{Acc.} & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Lexicalized}            & \t{??.?} & \t{79.4} & \t{82.3} & \t{80.9} & \t{78.2} \\
\t{Unigrams Only}          & \t{??.?} & \t{71.1} & \t{77.7} & \t{74.3} & \t{71.6} \\
\t{Unlexicalized}          & \t{??.?} & \t{56.0} & \t{64.4} & \t{59.9} & \t{50.39} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
Accuracy on the SNLI dataset, including precision/recall for the
  \textit{entailed} class on the test set.
Ablation results are reported for models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
\todo{fill in dev numbers}
}
\end{table}
%
% END BOW RESULTS TABLE
%

% Commenting out until PDF available. -S
% Running 'make' should generate PDF from gnuplot
\Fig{learning_curves_bow.pdf}{0.45}{bowlearncurve}{
A learning curve for the lexicalized and unlexicalized baseline classifiers,
plotted on a log scale.
Note the y axis starting at a random-chance accuracy of 33\%.
}

@@

% Insights 1: lexicalization helps a bunch
It is interesting to note the substantial jump in accuracy from using
  lexicalized features, and even from using the relatively sparse
  cross-bigram features.
In fact, the addition of these features alone allow the classifier to
  outperform the RTE baselines -- this is in some sense unsurprising:
  the RTE systems have been tuned on relatively small corpora
  (~1600 examples), whereas a classifier trained on SNLI can make use of
  over two orders of magnitude more data.

% Insights 2: the learning curve for the unlexicalized classifier is sad
More surprising is how quickly the lexicalized classifier outperforms its
  unlexicalized counterpart (see \reffig{bowlearncurve}).
With only 100 training examples, the cross-bigram classifier is already
  outperforming its unlexicalized counterpart.
Empirically we notice that the top weighted features for the classifier
  trained on 100 examples tend to be high precision entailments;
  e.g.,
  \textit{playing} $\rightarrow$ \textit{outside}
  (most scenes are outdoors), or \textit{a banana} $\rightarrow$
  \textit{person eating}.
If relatively few spurious entailments get high weight -- as it appears
  is the case -- then it makes sense that when these do fire they
  provide some boost in accuracy.
